---
title: "P8105 Homework 1"
author: "xj2357"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains body measurements for penguins from
the Palmer Archipelago, Antarctica. It has `r nrow(penguins)`
observations and `r ncol(penguins)` variables.

The species are Adelie, Chinstrap, and Gentoo, and the islands are 
Biscoe, Dream, and Torgersen. Measurements include bill length,
bill depth, and flipper length in millimeters, and body mass in grams.
The dataset also records sex and year.

The mean flipper length is
`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)`
mm, excluding missing values.

## Scatterplot

```{r penguin_scatterplot, fig.width = 6, fig.height = 4}
penguin_plot = ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point(na.rm = TRUE) +
  labs(
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    color = "Species"
  )

penguin_plot
```

Observations with missing bill length or flipper length are omitted
from this plot.

```{r save_penguin_plot}
ggsave(
  filename = "penguin_scatterplot.png",
  plot = penguin_plot,
  width = 6,
  height = 4,
  units = "in",
  dpi = 300
)
```

# Problem 2

