---
title: "P8105 Homework 1"
author: "xj2357"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

The `penguins` dataset contains body measurements for penguins from
the Palmer Archipelago, Antarctica. It has `r nrow(penguins)`
observations and `r ncol(penguins)` variables.

The species are Adelie, Chinstrap, and Gentoo, and the islands are 
Biscoe, Dream, and Torgersen. Measurements include bill length,
bill depth, and flipper length in millimeters, and body mass in grams.
The dataset also records sex and year.

The mean flipper length is
`r round(mean(pull(penguins, flipper_length_mm), na.rm = TRUE), digits = 2)`
mm, excluding missing values.

## Scatterplot

```{r penguin_scatterplot, fig.width = 6, fig.height = 4}
penguin_plot = ggplot(
  penguins,
  aes(
    x = bill_length_mm,
    y = flipper_length_mm,
    color = species
  )
) +
  geom_point(na.rm = TRUE) +
  labs(
    x = "Bill length (mm)",
    y = "Flipper length (mm)",
    color = "Species"
  )

penguin_plot
```

Observations with missing bill length or flipper length are omitted
from this plot.

```{r save_penguin_plot}
ggsave(
  filename = "penguin_scatterplot.png",
  plot = penguin_plot,
  width = 6,
  height = 4,
  units = "in",
  dpi = 300
)
```

# Problem 2

## Create the data frame

The data frame below contains a standard normal sample, an indicator
of whether each sampled value is positive, a character vector,
and a factor with three levels.

```{r create_example_df}
set.seed(1)

example_df = tibble(
  normal_sample = rnorm(10),
  is_positive = normal_sample > 0,
  text_value = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  category = factor(
    c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A"),
    levels = c("A", "B", "C")
  )
)

example_df
```

## Means of different variable types

```{r variable_means}
mean(pull(example_df, normal_sample))
mean(pull(example_df, is_positive))
mean(pull(example_df, text_value))
mean(pull(example_df, category))
```

The numeric and logical variables have valid means. For the logical
variable, TRUE is treated as 1 and FALSE as 0, so its mean is the
proportion of sampled values greater than zero.

The character and factor variables return NA with warnings because
these variables are not numeric or logical.

argument is not numeric or logical: returning NA
